---
title: "Distribution"
---

The performance of Africa's power supply sector on the continent is woefully unsatisfactory. Most of the continent's power companies are unreliable sources of supply, inefficient users of generating capacity, deficient in maintenance, erratic in the procurement of spare parts, and unable to staunch losses in transmission and distribution. They also have failed to provide adequate electricity services to the majority of the region's population, especially to rural communities, the urban poor, and small and medium enterprises.

A video on *Electriciy Is Holding Africa Back* [documentation](https://www.youtube.com/watch?v=OO_o6qNelM4%7D.%22)









### Electricity Distribution Across Africa


About 30% of people in Sub-Saharan Africa have access to grid electricity, the lowest of any major region in the world. Sub-Saharan Africans consume only one fifth the grid electricity of the global average of grid electricity.People who do not have it must rely on expensive diesel generators, kerosene lamps, candles, or firewood. Without electricity, one cannot use electric appliances, which are the foundation of both large and small-scale modern industry.










#### <small> This is a table showing electricity distribution in Africa

```{r}
library(rnaturalearth)
library(tidyverse)
#plot(ne_countries(continent = "Africa"))

africa <- ne_countries(continent = "Africa")
electricity <- read_csv("International Energy Agency - Total electricity production, Africa.csv")
africa <- africa |> 
  select(sov_a3, name_long)

africa_electricity <- left_join(africa, electricity, by = join_by("sov_a3" =="ISO3")) |>
  filter(!is.na(Electricity))


ggplot(data = africa_electricity) +
  geom_col(mapping = aes(y=sov_a3, x= Electricity))

```

##### <small> This Map shows electricity consumptions in 2023

```{r}
ggplot(data = africa_electricity) +
  geom_sf(aes(fill=Electricity)) +
  theme_minimal() +
   scale_colour_viridis_d()
  
```
